---
title: "Alcohol vs Seat choice"
author: "Irene Garcia"
date: "Sept 14 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
On the boxplot for the people that sit in the back we can see that they drink more drinks per week. The top of the box hits at about 12.5 drinks per week that would be the 75th percentile of the back row. The front row shows they drink 2 drinks per week. The middle row drink 4 drinks per week. That plot supports the idea that the back row drinks more than anyone sitted anywhere else. 



## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The people that sit in the back seat drink about 8.5 drinks per week. The people in the front seats drink about 1.78 drinks per week. The people in the middle seats drink about 3.33 drinks per week. We can see here that the people in the back drink the most and the people in the front drink the least. 

## Inferential Tests
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```
The p value is at 0.000116. If the null hypothesis is true and the chances of getting the sample is very small so I reject the null hypothesis. 

```{r}
plot(TukeyHSD(model1))
```

There appears to be no difference between the middle and the back when we see 0 in the confidence interval however 0 is not in the confidence interval for the front- back and middle - back.

## Conclusions

The plots, numerical results, and the inferential results show us that there is a difference between the drinking in the back, middle and front row.The real difference is between the back and the other two rows.  
