---
title: "Alcohol vs Seat choice"
author: "Irene Garcia"
date: "Sept 14 2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

## Numerical Summarys 
```{r}
favstats(alcohol~Seat,data=ucdavis1)
```
The people that sit in the back seat drink about 8.5 drinks per week. The people in the front seats drink about 1.78 drinks per week. The people in the middle seats drink about 3.33 drinks per week. We can see here that the people in the back drink the most and the people in the front drink the least. 

## Inferential Tests

## Conclusions


